Instructions for Authors

### 2012-03-21 paper/vago.uai/paper.tex
corrected version

\begin{crl}
An upper bound on the VOI estimate $\Lambda_i^b$ is obtained
by substituting (\ref{eqn:probound-blnk-hoeffding}) into (\ref{eqn:thm-be}).
\begin{align}
  \label{eqn:bound-blnk-hoeffding}
  \Lambda&_\alpha^b \le \hat\Lambda_\alpha^b=\frac {2N\overline X_\beta^{n_\beta}} {n_\alpha}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})^2 n_\alpha\right)\nonumber\\
  \Lambda&_{i|i\ne\alpha}^b\le \hat\Lambda_i^b=  \frac {2N(1-\overline  X_\alpha^{n_\alpha})} {n_i}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})^2 n_i\right)
\end{align}
\label{crl:bound-blnk-hoeffding}
\end{crl}
\vspace{-2em}
Better bounds can be obtained through tighter estimates on the
probabilities, for example, based on the empirical Bernstein
inequality~\cite{MaurerPontil.benrstein}, or through a more careful
application of the Hoeffding inequality.

@@

The sampling policies are first compared on random Multi-armed bandit 
problem instances. Figure~\ref{fig:random-instances} shows results for
randomly-generated Multi-armed bandits with 32 Bernoulli arms, with
the mean rewards of the arms distributed uniformly in the range~$[0,
  1]$, for a range of sample budgets~$32..1024$, with multiplicative
step of~$2$. The experiment for each number of samples was repeated
10000 times. UCB1 is always considerably worse than the
VOI-aware sampling policy.

>>>>

\begin{crl}
An upper bound on the VOI estimate $\Lambda_i^b$ is obtained
by substituting (\ref{eqn:probound-blnk-hoeffding}) into (\ref{eqn:thm-be}).
\begin{align}
  \label{eqn:bound-blnk-hoeffding}
  \Lambda&_\alpha^b \le \hat\Lambda_\alpha^b=\frac {2N\overline X_\beta^{n_\beta}} {n_\alpha}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})^2 n_\alpha\right)\nonumber\\
  \Lambda&_{i|i\ne\alpha}^b\le \hat\Lambda_i^b=  \frac {2N(1-\overline  X_\alpha^{n_\alpha})} {n_i}\exp\left(- \varphi(\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})^2 n_i\right)
\end{align}
\label{crl:bound-blnk-hoeffding}
\end{crl}
\vspace{-2em}
Better bounds can be obtained through tighter estimates on the
probabilities, for example, based on the empirical Bernstein
inequality~\cite{MaurerPontil.benrstein}, or through a more careful
application of the Hoeffding inequality:
\begin{align}
\Lambda_i^b&\le\frac {N\sqrt \pi} {n_i \sqrt {n_i}}
  \left[\mathrm{erf}\left((1\hspace{-0.25em}-\hspace{-0.25em}\overline X_i^{n_i})\sqrt {n_i}\right)
      \hspace{-0.25em}-\hspace{-0.25em}\mathrm{erf}\left((\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_i^{n_i})\sqrt{n_i}\right)\right]\nonumber\\
\Lambda_\alpha^b&\le\frac {N\sqrt \pi} {n_\alpha \sqrt {n_\alpha}}
  \left[\mathrm{erf}\left(\overline X_\alpha^{n_\alpha}\sqrt {n_\alpha}\right)
      -\mathrm{erf}\left((\overline X_\alpha^{n_\alpha}\hspace{-0.5em} - \overline X_\beta^{n_\beta})\sqrt{n_\alpha}\right)\right]
\label{eqn:erf-blinkered}
\end{align}

@@

The sampling policies are first compared on random Multi-armed bandit 
problem instances. Figure~\ref{fig:random-instances} shows results for
randomly-generated Multi-armed bandits with 25 Bernoulli arms, with
the mean rewards of the arms distributed uniformly in the range~$[0,
  1]$, for a range of sample budgets~$200..2000$, with multiplicative
step of~$2$. The experiment for each number of samples was repeated
10000 times. UCB1, as well as policies  based on bounds
(\ref{eqn:bound-blnk-hoeffding}) (VOI) and
(\ref{eqn:erf-blinkered}) (VOI+) are compared. UCB1 is always considerably worse than the
VOI-aware sampling policies.
